\documentclass[12pt]{article}
\usepackage[english]{babel}
%\usepackage[utf8x]{inputenc}
%\usepackage{amsmath}
%\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}
\usepackage{sectsty}

\makeatletter
\def\@seccntformat#1{%
  \expandafter\ifx\csname c@#1\endcsname\c@section\else
  \csname the#1\endcsname\quad
  \fi}
\makeatother

\allsectionsfont{\centering}	

\begin{document}

\begin{titlepage}

 % Defines a new command for the horizontal lines, change thickness here
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

 % Center everything on the page
\center
 
%----------------------------------------------------------------------------------------
%	HEADING SECTIONS
%----------------------------------------------------------------------------------------

\textsc{\LARGE Hunter College}\\[1.5cm] 
\textsc{\Large Computer Science}\\[0.5cm] 
\textsc{\large }\\[0.5cm]

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\HRule \\[0.4cm]
% Title of your document
{ \huge \bfseries RaceMe}\\[0.4cm] 
\HRule \\[1.5cm]
 
%----------------------------------------------------------------------------------------
%	AUTHOR SECTION
%----------------------------------------------------------------------------------------

\begin{minipage}{0.4\textwidth}
\begin{center} \large
\emph{Created By}\\
\textsc{Jason Lizhou Cheng Satbir Itzhak}
\end{center}
\end{minipage}\\[2cm]

%----------------------------------------------------------------------------------------
%	DATE SECTION
%----------------------------------------------------------------------------------------

% Date, change the \today to a set date if you want to be precise
{\large \today}\\[2cm] 


\end{titlepage}

\begin{abstract}

Many people surrender to the modern fast pace of life, placing their health and body second to societal demands. This is a pity since with a daily routine of 30 minutes of running, one can contribute to his/her health, be more productive and eliminate daily stress. By introducing runners with proper incentives (competition and achievements) to conduct along with fitness activity, alongside with the ability to see their progress as well as socialize, they can feel more accomplished and motivated to exercise. Hence, potential and current runners will find running an enjoyable necessity, and improvement in life.

\vspace{5mm}

Many people surrender to the modern fast pace of life, placing their health and body second to societal demands. This is a pity since with a daily routine of 30 minutes of running, one can contribute to his/her health, be more productive and eliminate daily stress. By introducing runners with proper incentives (competition and achievements) to conduct along with fitness activity, alongside with the ability to see their progress as well as socialize, they can feel more accomplished and motivated to exercise. Hence, potential and current runners will find running a more enjoyable and fulfilling activity.

\end{abstract}

\tableofcontents

\section{Introduction}

Your introduction 

\subsection{Introduction B}

Introduction Part 2

\end{document}